%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page
% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
\addtolength{\topmargin}{-.0in}
\usepackage{eurosym}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{14pt}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...
\usepackage[bottom]{footmisc}
\usepackage{multicol}
\usepackage{import}
\usepackage{etoolbox}
\usepackage{bbding}
\usepackage[misc]{ifsym}
\usepackage{fontawesome}
\makeatletter

% personal data
\makeatletter
\renewcommand*{\maketitle}{%
  \setlength{\maketitlewidth}{\textwidth}%
  \hfil%
  \parbox{\maketitlewidth}{%
    \centering%
    % name and title
    \namestyle{\@firstname~\@lastname}%
    \ifthenelse{\equal{\@title}{}}{}{\titlestyle{~|~\@title}}\\% \isundefined doesn't work on \@title, as LaTeX itself defines \@title (before it possibly gets redefined by \title) 
    % detailed information
    \addressfont\color{color2}%
    \ifthenelse{\isundefined{\@addressstreet}}{}{\addtomaketitle{\addresssymbol\@addressstreet}%
      \ifthenelse{\equal{\@addresscity}{}}{}{\addtomaketitle[~--~]{\@addresscity}}% if \addresstreet is defined, \addresscity and \addresscountry will always be defined but could be empty
      \ifthenelse{\equal{\@addresscountry}{}}{}{\addtomaketitle[~--~]{\@addresscountry}}%
      \flushmaketitle\@firstmaketitleelementtrue\\}%
    \collectionloop{phones}{% the key holds the phone type (=symbol command prefix), the item holds the number
      \addtomaketitle{\csname\collectionloopkey phonesymbol\endcsname\collectionloopitem}}%
    \ifthenelse{\isundefined{\@email}}{}{\addtomaketitle{\emailsymbol\emaillink{\@email}}}%
    \ifthenelse{\isundefined{\@homepage}}{}{\addtomaketitle{\homepagesymbol\httplink{\@homepage}}}%
    \collectionloop{socials}{% the key holds the social type (=symbol command prefix), the item holds the link
      \addtomaketitle{\csname\collectionloopkey socialsymbol\endcsname\collectionloopitem}}%
    \ifthenelse{\isundefined{\@extrainfo}}{}{\addtomaketitle{\@extrainfo}}%
    \flushmaketitle}\\[2.5em]}% need to force a \par after this to avoid weird spacing bug at the first section if no blank line is left after \maketitle

 \makeatother
\name{\hspace*{-1.37cm} Lachlan}{Marnham}

\title{Curriculum Vitae}

%\address{Flat 4, 49 Kingsgate Road, London, United Kingdom, NW6 4TD}{}{} 

\extrainfo{\hspace*{-2.2cm} \faGlobe \space \href{www.lachlanmarnham.com}{lachlanmarnham.com} | \faGithub \space \href{https://github.com/LachlanMarnham}{LachlanMarnham} | \faEnvelope \space \href{mailto:lachlan.marnham@gmail.com}{lachlan.marnham@gmail.com} | \faMobile \space +44 (0)7856516125 }
\begin{document}

\makecvtitle

\vspace{-0.9cm}

\section{At a Glance}
\small{I am a backend software engineer with a focus on the design and implementation of services in the cloud. My background is in theoretical physics and the video-conferencing industry. I aspire to be the kind of specialist who is capable of proficiently building technologies outside of my speciality.}

\begin{itemize}
\item{\small{\textbf{Primary Language:} Python}}
\item{\small{\textbf{Other Languages:} SQL, Go, JavaScript, HTML, CSS}}
\item{\small{\textbf{Process:} Linux, git, unit testing, system testing, continuous integration, code review}}
\item{\small{\textbf{Communication:} Journal publication, \LaTeX, magazine writing, university teaching, conference presentation}}
\item {\small{\textbf{Spoken Language:} English (native proficiency)}}
\item {\small{\textbf{Citizenship:} Irish and Australian (dual citizenship)}}
\end{itemize}

\section{Experience}
\begin{itemize}
\item{\cventry{\small{April 2017--present}}{\small{Software Engineer}}{StarLeaf}{London, UK}{}{
\small{
\begin{itemize}
\item \textbf{Backend Engineering of a Cloud Videoconferencing Platform}
\item \textbf{Skills Developed:} Python, SQL, JavaScript, HTML, CSS, RESTful API design, distributed systems engineering, service architecture design, unit and system testing, development of a multi--versioned cloud infrastructure, continuous integration, software planning and specification, test plan writing and working with large and complex code bases.
\item \textbf{Achievements: }
\begin{itemize}
\item Designed and built a bespoke infrastructure system--testing platform. This involved the remote control of virtual StarLeaf video conferencing and instant messaging clients to probe a cloud with dozens of constituent server species.
\item Implemented a distributed, co--located database and database--control infrastructure for the storage and pipelining of customer product--usage data. This system was written in such a way so as to allow for customer data to be stored in a jurisdiction of their choice, while enabling the data to be accessed transiently by credentialed team members. I also worked on a suit of internal tools for the categorization and display of this information.
\item Developed a platform which serves dashboards to customers, allowing them to view product--usage statistics in real time.
\end{itemize}
\end{itemize}
}}}
\item{\cventry{\small{April 2012--2016}}{\small{Doctoral Researcher}}{University of Exeter}{Exeter, UK}{}{\small{
\begin{itemize}
\item \textbf{Low-dimensional Condensed Matter Field Theory and Applications}
\item {\textbf{Skills Developed:} Python, Mathematica, computational mathematics, pair programming, code review, version control, complex analysis, field theory, graph theory, group theory, multivariate calculus, linear algebra, topology and academic communication (conference speaking, publication in journals, teaching, writing textbook reviews and so on).} 
\item \textbf{Achievements: } 
\begin{itemize}
\item Developed a mathematical and conceptual framework for the formation of particles composed of electron pairs in certain low--dimensional systems.
\item Published in peer--reviewed journals.
\item Taught a variety of problems classes and tutorials in physics and mathematics.
\item Won two research prizes, and was twice nominated for a graduate teaching prize.
\end{itemize}
\end{itemize}
}}}

\end{itemize}
\pagebreak
\section{Education and Research}

\begin{itemize}
\small{
\item{\cventry{\small{2012--2016}}{\small{PhD Theoretical Physics}}{University of Exeter}{Exeter, UK}{}{\small{Graduated December 2016}}}

\item{\cventry{\small{2011--2012}}{\small{Honours Year (Masters), Physics, 1st Class Honours, Distinction}}{University of Wollongong}{Wollongong, Australia}{}{\small{Dissertation grade: 96\% -- Overall Masters Grade: 93\%}}}  % arguments 3 to 6 can be left empty

\item{\cventry{\small{2008--2012}}{\small{BSc Advanced (Physics), 1st Class Honours, Distinction}}{University of Wollongong}{Wollongong, Australia}{}{\small{Degree Average: 87\%}}}  % arguments 3 to 6 can be left empty
}
\end{itemize}

\subsection{Major Research Projects}

\begin{itemize}
\small{
\item{\textbf{Doctoral Project:} \textit{\small{`Anomalous Electron Pairing in Graphene'}}
\small{\begin{itemize}
\item Computational work performed mostly in Python (some Mathematica) with NumPy and SciPy, with all coding and algorithm design developed from scratch.
\item Development and application of novel low-dimensional quantum condensed-matter field theories to the study of mesoscopic systems.
\item Lead to the proposal of a new kind of (quasi)particle in graphene
\end{itemize}}}
\item{\textbf{Masters Project:}\textit{\small{`Energy relaxation rate of an external electron due to plasma oscillations in a 2DEG with Rashba spin--orbital coupling', }}\small{Dissertation grade: 96\% -- Overall Masters Grade: 93\%}
\small{\begin{itemize}
\item All code developed from scratch in C++
\item This work studied electron transport normal to semiconductor heterojunctions with Rashba spin-orbit coupling
\item Applications in the area of energy loss in spintronic nanostructures
\end{itemize}}}}
\end{itemize}

\subsection{Publications}

\begin{itemize}
\small{
\item{\textbf{Metastable electron--electron states in double--layer graphene structures}\\
      \textcolor{blue}{\underline{\href{https://arxiv.org/abs/1410.0864}{\small{arXiv:1410.0864v2 [cond-mat.mes-hall]}}}}}

\vspace{4pt}

\item{\textbf{Bielectrons in the Dirac sea in graphene: the role of many–body effects}\\
		\textcolor{blue}{\underline{\href{http://arxiv.org/abs/1512.02953}{\small{arXiv:1512.02953 [cond-mat.mes-hall]}}}}}
\small}
\end{itemize}

\section{Open Source}

\small{
\subsection{Major Contributions or Sole Contributor}
\begin{itemize}
\item \textbf{Anar$\chi$iv: } The initial phase of this project, which I am working on with two co--founders, is an interactive feedback platform which sits on top of the Ar$\chi$iv pre-print repository. Our long--term goal is to build it out into an open source, free-to-publish \textit{and} free-to-read academic journal.
\item \textbf{Partita: } Musical instrument practice assistant, incorporating progress tracking and spaced repetition, metronome and tuner. Currently for desktop, but will eventually ship as a web app.
\item \textbf{Lethe: } A stateless, deterministic password manager. Generates strong passwords at run time, and doesn't store them \textit{anywhere}, but generates the same passwords with every use.
\end{itemize}

\subsection{Just Helping Out}

\begin{itemize}
\item \textbf{Sucuri: } A HTML templating engine.
\item \textbf{tldr: } Simplified \verb|man| pages which only list the few use cases the user is most likely to need.
\end{itemize}
}

\section{Honours and Awards}

\begin{itemize}\small{
\item{\textbf{Exeter Students’ Guild Teaching Awards} \small{(twice nominated) \textit{``Category: Best Graduate Teaching Assistant''}}}
\item{\textbf{University of Exeter Early Careers Network Poster Prize} \small{(2015) \textit{``1st place''}}}
\item{\textbf{Europhysics Letters Prize} \small{(2013) \textit{``In recognition of the best presentation at GrapheneWeek 2013''}}}
\item{\textbf{College Research Studentship}\small{ (2012--2016)}}
\item{\textbf{Physics Engineering Discipline Prize} \small{(2010, 2011 and 2012) \textit{``For best performance in physics''}}}
\item{\textbf{University of Wollongong Dean's Merit List}\small{ (2010, 2011 and 2012)}}
\item{\textbf{Kittel--Lewis Prize for Solid State Physics}\small{ (2011) \textit{``For best performance in Solid State Physics''}}}}
\end{itemize}

\section{Other Interests}

\begin{center}
Classical guitar, recording and performance | Hiking | Reading | Tech meet--ups
\end{center}
%\pagebreak

%\section{References}

%\vspace{5pt}

%\begin{itemize}
%\item{\textbf{Dr. Sharon Strawbridge (My Module Leader for Natural Sciences Tutoring)}\\
%		Senior Lecturer of Physics and Chemistry\\
%		School of Physics, University of Exeter,\\
%		Stocker Road, Exeter, UK, EX4 4QL.\\
%		\Phone\thinspace+44 1392 725189\\
%		\Letter\thinspace\textcolor{blue}{\underline{\href{mailto:S.M.Strawbridge@exeter.ac.uk}{ S.M.Strawbridge@exeter.ac.uk}}}}

%\vspace{6pt}

%\item{\textbf{Dr. Jacopo Bertolotti (My Module Leader for Mathematics with Physical Applications Demonstrating)}\\
%		Lecturer of Physics\\
%		School of Physics, University of Exeter,\\
%		Stocker Road, Exeter, UK, EX4 4QL.\\
%		\Phone\thinspace+44 1392 725695\\
%		\Letter\thinspace\textcolor{blue}{\underline{\href{mailto:S.M.Strawbridge@exeter.ac.uk}{J.Bertolotti@exeter.ac.uk}}}}

%\vspace{6pt}		

%\item{\textbf{Dr. Andrey Shytov (My PhD Supervisor)}\\
%		Lecturer of Physics\\
%		School of Physics, University of Exeter,\\
%		Stocker Road, Exeter, UK, EX4 4QL.\\
%		\Phone\thinspace+44 1392 722169\\
%		\Letter\thinspace\textcolor{blue}{\underline{\href{mailto:A.Shytov@exeter.ac.uk}{A.Shytov@exeter.ac.uk}}}}

%\vspace{6pt}

%\item{\textbf{Dr. Marcin Mucha-Kuczynski (My Thesis Examiner and Collaborator)}\\
%		Assistant Professor of Physics\\
%		Department of Physics, University of Bath,\\
%		Claverton Down, Bath, UK, BA2 7AY.\\
%		\Phone\thinspace+44 1225 385543\\
%		\Letter\thinspace\textcolor{blue}{\underline{\href{mailto:M.Mucha-Kruczynski@bath.ac.uk}{M.Mucha-Kruczynski@bath.ac.uk}}}}

%\vspace{6pt}

%\item{\textbf{Prof. Chao Zhang (My Masters Supervisor; Was Also My Statistical Mechanics, Thermodynamics and Quantum Mechanics Professor)}\\
%		Professor of Physics, Coordinator of Solid State Research Program \\
%		Institute of Superconducting and Electronic Materials, University of Wollongong,\\
%		Northfields Ave, Wollongong, New South Wales, Australia, 2522.\\
%		\Phone\thinspace+61 2 4221 3458\\
%		\Letter\thinspace\textcolor{blue}{\underline{\href{mailto:Chao_Zhang@uow.edu.au}{chao\_zhang@uow.edu.au}}}}

%\vspace{6pt}

%\item{\textbf{Prof. Roger Lewis (My Undergraduate Solid State Physics Professor)}\\
		%Professor of Physics, Chair of Faculty of Engineering Research Committee\\
		%Institute of Superconducting and Electronic Materials, University of Wollongong,\\
		%Northfields Ave, Wollongong, New South Wales, Australia, 2522.\\
		%\Phone\thinspace+61 2 4221 3518\\
		%\Letter\thinspace\textcolor{blue}{\underline{\href{mailto:roger_lewis@uow.edu.au}{roger\_lewis@uow.edu.au}}}}

%\end{itemize}

% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{plain}
%\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

%-----       letter       ---------------------------------------------------------

\end{document}


%% end of file `template.tex'.
